Model Search in Relational Domains

### 2016-10-20 experiments.tex
decision heuristics

\paragraph {\textbf{Decision Heuristics}} We compare the performance of 
different decision heuristics in ACDCL.  We observe that the ordered heuristic 
outperforms other heuristics on control-intensive benchmarks due to its 
ability to prioritize decisions on variables that appear in conditional 
branches.  For straight-line code and most of the bit-vector regression 
suite, random heuristics performs the best.  Whereas activity-based 
heuristics such as Berkmin heuristic which works well in propositional 
cases performs best for benchmarks that encountered \pscmt{???} the maximum number 
of conflicts to prove safety, thus allowing the heuristics \pscmt{???} to choose  
the decison variable among the set of learnt clauses.

\paragraph {\textbf{Propagation Strategy}}      
Figure~\ref{prop-dec} presents a comparison between {\em forward} propagation 
strategy and {\em multi-way} propagation strategy in ACDCL.  The choice of 
propagation strategy influences the total number of decisions and clause 
learning iterations.  Hence, the propagation strategy has a significant 
influence on the run time which can be visualised in Figure~\ref{prop-dec}.  
Unlike the forward propagation, the multi-way strategy may take several 
iterations to reach the fixed-point, but it significantly reduces the 
total number of decisions and conflicts.  This is attributed to the higher 
precision of the meet irreducibles inferred by the multi-way strategy which 
subsequently aids the decision heuristics to make better decisions. 
\Omit {
We observe that the deductions made during chaotic analysis helps the decision 
heuristics to make better decisions compared to forward analysis.  This is 
attributed to the precision of deductions inferred by the chaotic analysis.         
}

>>>>

\paragraph {\textbf{Propagation Strategy}}      
Figure~\ref{prop-dec}(a) presents a comparison between {\em forward} propagation 
strategy and {\em multi-way} propagation strategy in ACDCL.  The choice of 
propagation strategy influences the total number of decisions and clause 
learning iterations.  Hence, the propagation strategy has a significant 
influence on the run time which can be visualised in Figure~\ref{prop-dec}.  
Unlike the forward propagation, the multi-way strategy may take several 
iterations to reach the fixed-point, but it significantly reduces the 
total number of decisions and conflicts.  This is attributed to the higher 
precision of the meet irreducibles inferred by the multi-way strategy which 
subsequently aids the decision heuristics to make better decisions. 
\Omit {
We observe that the deductions made during chaotic analysis helps the decision 
heuristics to make better decisions compared to forward analysis.  This is 
attributed to the precision of deductions inferred by the chaotic analysis.         
}

\paragraph {\textbf{Decision Heuristics}} Figure~\ref{prop-dec}(b) presents a 
visualization of different decision heuristics in ACDCL.  We observe that 
the ordered heuristic outperforms other heuristics due to its ability to 
prioritize decisions on meet irreducibles that appear in conditional 
branches.  For straight-line code and most of the bit-vector regression 
suite, random heuristics performs the best.

\Omit{
Whereas activity-based heuristics such as Berkmin heuristic which 
works well in propositional cases performs best for benchmarks 
that encountered the maximum number of conflicts to prove safety, 
thus allowing the heuristics to choose the decison variable among the set of learnt clauses.   
}
